### 2015-05-18 paper/paper.tex
Added data table

>>>>

Implementation of the database for the given Monash IRT data was all performed using MongoDB version 3.0.3, the latest
version as of 2015-05-18. Interaction with the MongoDB database was all performed using the mongo shell and corresponding
official NodeJS MongoDB driver.

\subsection{Overview of the data} % (fold)
\label{sub:overview_of_the_data}

The test data used for this case study was acquired from the Monash IRT team, and was an extract of real data they have
received from the railway sensors. As only one set of data was given, simulated datasets based upon the extract have
also been created to simulate the type of inconsistencies the IRT team are facing, including differently structured
datasets and datasets with missing data (in the case of non-functional sensors).

The dataset received from the IRT team has the layout as shown in~\tabref{tab:irt_data}. It consists of 99999 data points
recorded at different times. The data received in this dataset is all consistent and contains readings from all the sensors.
As this is not the case in with real data over time, simulated data has been used as stated previously. The only
guaranteed data to be received is the \textbf{Time}, \textbf{Lat}, and \textbf{Lon} sensor recordings.

\begin{table}[h]
\caption{The different types of data received from the Monash University Institute of Railway Technology team.}
\label{tab:irt_data}
\tabcolsep=0.11cm
\scalebox{0.7}{
\begin{tabular}{ | l | l | l | }

\hline
\textbf{Data name}      & \textbf{Possible values}               & \textbf{Meaning} \\ \hline
\textbf{Time}           & Floating point value                   & Time in milliseconds since... \\ \hline
\textbf{Speed}          & Floating point value                   & Speed in km/h (?)  \\ \hline
\textbf{LoadEmpty}      & -1, 0                                  & Boolean flag denoting whether or not load is present in train cars.  \\ \hline
\textbf{km}             & Floating point value                   & Amount of kilometres travelled since...  \\ \hline
\textbf{Lat}            & Floating point value from -90 to +90   & Geographic latitude coordinate at given reading.  \\ \hline
\textbf{Lon}            & Floating point value from -180 to +180 & Geographic longitude coordinate at given reading.  \\ \hline
\textbf{Track}          & Integer value from 1 to 213841         & Given track in which the train is located.   \\ \hline
\textbf{SND1}           & Floating point value                   & ?  \\ \hline
\textbf{SND2}           & Floating point value                   & ?  \\ \hline
\textbf{SND3}           & Floating point value                   & ?  \\ \hline
\textbf{SND4}           & Floating point value                   & ?  \\ \hline
\textbf{CouplerForce}   & Floating point value                   & The amount of force couple detected in the train car.  \\ \hline
\textbf{LateralAccel}   & Floating point value                   & The amount of lateral acceleration detected in the train car.  \\ \hline
\textbf{AccLeft}        & Floating point value                   & The amount of acceleration detected by the left sensor.  \\ \hline
\textbf{AccRight}       & Floating point value                   & The amount of acceleration detected by the right sensor.  \\ \hline
\textbf{BounceFront}    & Floating point value                   & The amount of bounce detected at the front of the car.  \\ \hline
\textbf{BounceRear}     & Floating point value                   & The amount of bounce detected at the rear of the car.  \\ \hline
\textbf{RockFront}      & Floating point value                   & The amount of rock detected at the front of the car.  \\ \hline
\textbf{RockRear}       & Floating point value                   & The amount of rock detected at the front of the car.  \\ \hline

\end{tabular}}
\end{table}

% subsection overview_of_the_data (end)
